NoTitle

### 2017-05-22 SpringerLNCS/sections/Formalization.tex
change format to Springer LNCS
proof

\subsection{Syntax}
Figure~\ref{fig:syntax} shows the syntax of MIM. The multiple inheritance feature
of MIM has a basis on Java interfaces. To demonstrate how unintentional method conflicts
are untangled in MIM, we present the calculus in a straightforward way, hence we only
focus on a small subset of the interface model. For example, all the methods declared in an
interface are default methods, that is to say, they always provide default implementations.
From this point we can view that we are actually modelling a class model that supports multiple
inheritance. Then it is straightforward to do object creation like ``\new I''. Fields and
primitive types are not modelled as well.

@@

\newpage

@@

@@

>>>>

\subsection{Syntax}
Figure~\ref{fig:syntax} shows the syntax of MIM. The multiple inheritance feature
of MIM has a basis on Java interfaces. To demonstrate how unintentional method conflicts
are untangled in MIM, we present the calculus in a straightforward way, hence we only
focus on a small subset of the interface model. For example, all the methods declared in an
interface are default methods, that is to say, they always provide default implementations.
From this point we can view that we are actually modelling a class model that supports multiple
inheritance. Then it is straightforward to do object creation like $\new I$. Fields and
primitive types are not modelled as well.

@@

@@

\begin{lemma}~\label{lamma0}
$\textit{If } \mtype(m, I, J) = \overline{D} \rightarrow D, \textit{ and } \mbody(m, I, J) = \overline{x}.e, 
 \textit{ then for some } J_0 \textit{ with } I <: J_0, \  \exists C <: D, \textit{ such that }  
 \judgeewf {\overline{x}:\overline{D}, \kwthis:J_0} {e:C} $.
\end{lemma}

\begin{lemma}[Term Substitution Preserves Typing]~\label{lamma1}
$\textit{If } \ \judgeewf {\Gamma, \ \overline{x}:\overline{I_X}} { e : I } \textit{ , and }
\judgeewf {\Gamma} {\overline{y}:\overline{I_Y}} \textit{ where } \overline{I_Y} \subtype \overline{I_X}
\textit{, then } \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I'} \textit{ for some } I' \subtype I.
$
\end{lemma}

@@

\begin{proof} ~\\
\noindent \textbf{Case Invk.} 
let \[ e = <J>\new I.m(<\overline{I_E}>\overline{e}) \]	
Suppose \[ \mbody(m, I, J) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}, \; <J>\new I/\kwthis ] e_0 \] 
By rules (T-NEW) and (T-INVK), 
  \[ \judgeewf \Gamma {\new I:I} \quad 
	 \mtype(m, I, J) = \overline{I_X} \rightarrow I_{E_0} \quad 
	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
	 \overline{Y_E} \subtype \overline{X} \quad
	 \textit{, for some } \; \overline{Y_E}
  \]
By Lemma~\ref{lamma0},
	\[
	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } J \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
	\]
By Lemma~\ref{lamma1},
	\[
	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x}, \; <J>\new I/\kwthis ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
	\]
So $I_G <: I_{E_0}$, finally just let $I' = I_G$.

\noindent \textbf{Case PathInvk.}
let \[ e = <J>\new I.K::m(<\overline{I_E}>\overline{e}) \]	
Suppose \[ \mbody(m, I, K) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}, \; <K>\new I/\kwthis ] e_0 \] 
By rules (T-NEW) and (T-INVK), 
  \[ \judgeewf \Gamma {\new I:I} \quad 
	 \mtype(m, I, K) = \overline{I_X} \rightarrow I_{E_0} \quad 
	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
	 \overline{Y_E} \subtype \overline{X} \quad
	 \textit{, for some } \; \overline{Y_E}
  \]
By Lemma~\ref{lamma0},
	\[
	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } K \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
	\]
By Lemma~\ref{lamma1},
	\[
	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x}, \; <K>\new I/\kwthis ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
	\]
So $I_G <: I_{E_0}$, finally just let $I' = I_G$.

\noindent \textbf{Case Super-Invk.}
let \[ e = \kwsuper.K::m(<\overline{I_E}>\overline{e}) \]	
Suppose \[ \mbody(m, K, K) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}] e_0 \] 
By rules (T-NEW) and (T-INVK), 
  \[ 
	 \mtype(m, K, K) = \overline{I_X} \rightarrow I_{E_0} \quad 
	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
	 \overline{Y_E} \subtype \overline{X} \quad
	 \textit{, for some } \; \overline{Y_E}
  \]
By Lemma~\ref{lamma0},
	\[
	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } K \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
	\]
By Lemma~\ref{lamma1},
	\[
	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x} ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
	\]
So $I_G <: I_{E_0}$, finally just let $I' = I_G$.

\end{proof}
